\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amssymb}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}

\begin{document}

\begin{flushleft}
Jack Al-Kahwati\\
StarDrive Research Group\\
San Francisco, CA 94102\\
\href{mailto:jack@thestardrive.com}{jack@thestardrive.com}
\end{flushleft}

\vspace{1em}
\today

\vspace{1em}
Editor, Physical Review D\\
American Physical Society

\vspace{1em}
Dear Editor,

\vspace{0.5em}
Please find enclosed our manuscript ``Boundary Phase Resonance: A Discrete Lattice Origin for the Standard Model Spectrum'' for consideration as a Regular Article in \textit{Physical Review D}.

The manuscript presents a framework in which Standard Model particle masses, mixing angles, and cosmological parameters emerge from a discrete $\mathbb{Z}_p$ lattice Hamiltonian on a boundary surface. From three substrate parameters and four fermion anchor masses (7 inputs total), we derive 50 quantitative predictions benchmarked against PDG, Planck, and CODATA data, all agreeing within $2\sigma$ (43 effective degrees of freedom).

Principal results include:
\begin{itemize}
\item Higgs boson mass to 0.04\% accuracy
\item Strange-to-down quark mass ratio $m_s/m_d = 20.0$ (exact match)
\item All three neutrino mixing angles within 0.3--0.6$\sigma$ of PDG values
\item Baryon asymmetry within 0.4$\sigma$ of Planck
\item Fine structure constant $\alpha^{-1} = 137.03$ from substrate parameters alone (32 ppm deviation from CODATA)
\end{itemize}

The framework makes six falsifiable predictions testable within five years, including normal neutrino ordering (JUNO), Dirac neutrinos (no $0\nu\beta\beta$ decay), and quadratic decoherence scaling in impedance mismatch. All derivations are implemented as open-source software with 500+ automated tests.

We believe this work is well suited to \textit{Physical Review D} given its focus on particle physics phenomenology, beyond-Standard-Model physics, and quantitative predictions. The manuscript has not been published elsewhere and is not under consideration at another journal.

We suggest the following PACS categories: 12.60.-i (Models beyond the standard model), 14.80.Bn (Standard-model Higgs bosons), 12.15.Ff (Quark and lepton masses and mixing), 14.60.Pq (Neutrino mass and mixing), 95.35.+d (Dark matter).

Thank you for your consideration.

\vspace{1em}
Sincerely,

\vspace{1em}
Jack Al-Kahwati

\end{document}
